\huge \systemEnding: Growing Libraries of Concepts with Wake-Sleep Program Induction

### 2018-07-23 misc2.tex
changes to poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Portrait Poster
% LaTeX Template
% Version 1.0 (31/08/2015)
% (Based on Version 1.0 (29/03/13) of the landscape template
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% Portrait version by:
% John Hammersley
%
% The landscape version of this template was downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    \includegraphics[width = 20cm]{figures/animation/DC.eps}

%% \begin{tikzpicture}[scale=4,line width=1.5mm]

%%   \node[latent,scale=3] at (3.5,3) (dx){$\mathcal{D}$};
%%   \node[latent,scale=3] at ([xshift=2cm]dx) (zp){$p_n$};
%%   \node[obs,scale=3] at ([xshift=2cm]zp) (xp) {$x_n$};
%%   \plate {}{(zp)(xp)}{};
%% %  \node[align = center] at ([yshift = -1.2cm,xshift = 1cm]xp.east) {(b) \\recognition model};
%%   \draw [->,red] (xp.south) to[out = -90,in = -90] node(nn){} (zp.south);
%% %  \draw [->,red] (tx.west) -- (zp.east);
%%   \draw [->] (dx.east) -- (zp.west);
%%   \draw [->] (zp.east) -- (xp.west);

%%   \node at (nn) {
%%     \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.5,shift={+(-1,2.5)}}]
%%       \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
%%       \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
%%       \node[rectangle] at (1,1) {};
%%       \foreach \name / \y in {1,...,4}
%%           \node[neuron] (I-\name) at (0,-\y) {};
%%       \foreach \name / \y in {1,...,3}
%%           \node[neuron] (H-\name) at (1,-\y-0.5) {};
%%       \foreach \name / \y in {1,...,4}
%%           \node[neuron] (O-\name) at (2,-\y) {};
%%       \foreach \source in {1,...,4}
%%           \foreach \dest in {1,...,3}
%%               \draw [-latex] (I-\source) -- (H-\dest);
%%       \foreach \source in {1,...,3}
%%           \foreach \dest in {1,...,4}
%%               \draw [-latex] (H-\source) -- (O-\dest);
%%     \end{tikzpicture}
%%   };
%%   \node[shift={+(0,-1.7)}] at (nn) { $Q$  };

%%   \end{tikzpicture}

  Observe \textbf{tasks} (program induction problems). 
  Solve tasks w/ latent programs.
  %% \textbf{Likelihood model} $\probability[x_n|p_n]$
  %% scores program $p_n$ on task $x_n$
  Latent  \textbf{DSL} acts as generative model over programs: `library of concepts'.
  \textbf{Recognition model}: a neural net that predicts distribution over programs conditioned on task: `procedural knowledge'

@@

\begin{block}{Wake: Problem solving}
  \begin{tikzpicture}[scale=2.5]
    \node at (0,0) (d){DSL};
    \node at ([yshift = -2cm]d) (t){$\text{Task}$};

@@

    \draw [->  ,rounded corners] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
%    \node at ([xshift = 0.5cm,yshift = -0.75cm]s.south) {Spec};

 %   \node at (4,-3.5) {\textbf{\textsc{Wake: Problem Solving}}};

@@

  Neural network
  predicts distribution over programs conditioned on tasks.
  Simple model: just predicts probabilities of DSL productions.  Goal: learn to invert generative model from (program, task) pairs

>>>>

s%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Portrait Poster
% LaTeX Template
% Version 1.0 (31/08/2015)
% (Based on Version 1.0 (29/03/13) of the landscape template
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% Portrait version by:
% John Hammersley
%
% The landscape version of this template was downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newcommand{\NeuralNetwork}[1]{    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=#1,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}}

\begin{tikzpicture}[scale=4,line width=1.5mm]

  \node[latent,scale=3] at (3.5,3) (dx){DSL};
  \node[latent,scale=3] at ([yshift=-1.5cm]dx) (zp){prog};
  \node[obs,scale=3] at ([yshift=-2cm]zp) (xp) {data};
  \node[latent,scale=3] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=3] at ([xshift=2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);
%  \node at (nn) {\NeuralNetwork{0.5}};

  \node[latent,scale=3] at ([xshift=-2cm]zp) (zp1){prog};
  \node[obs,scale=3] at ([xshift=-2cm]xp) (xp1) {data};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);
%  \node at (nn) {\NeuralNetwork{0.5}};

  \draw [->,red] (xp.east) to[out = 30,in = -30] node(nn){} (zp.east);
  \node at (nn) {\NeuralNetwork{0.5}};
  \draw [->] (dx.south) -- (zp.north);
  \draw [->] (zp.south) -- (xp.north);

  %\node[shift={+(0,-1.7)}] at (nn) { $Q$  };

  Observe program induction problems, 
  Solve  w/ latent programs.
  %% \textbf{Likelihood model} $\probability[x_n|p_n]$
  %% scores program $p_n$ on task $x_n$
  Latent  \textbf{DSL} acts as generative model over programs: `library of concepts'.
{\color{red}  \textbf{Recognition model}}: a neural net that predicts distribution over programs conditioned on task: `procedural knowledge'

@@

\begin{block}{Wake: Problem solving}
  \begin{tikzpicture}[scale=2.5,line width=1.3mm]
    \node at (0,0) (d){DSL};
    \node at ([yshift = -2cm]d) (t){$\text{Task}$};

@@

    \draw [->  ,rounded corners] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
  \end{tikzpicture}

@@

  %% Neural network
  %% predicts distribution over programs conditioned on tasks.
  %% Simple model: just predicts probabilities of DSL productions.  
  Goal: learn to invert generative model from (program, task) pairs
